\pagebreak
\hspace{0pt}
\vfill
\textbf{Abstract.}
Android is the most popular mobile Operating System in the world and it dominates the market share, which makes it an important platform for developers to publish applications (apps). Moreover, nowadays, there is an enormous amount of apps available and a part of them is developed by programmers which are not trained to code in a secure manner, leading to user's privacy leakages. Moreover, developers have a hard time finding resources on-line, to avoid common security mistakes. The phenomenon of exploited apps is also growing, despite the effort of Google, which only put in place a layer of automatic testing proved to be insufficient\cite{bouncerfail}. Therefore, we present and evaluate here \emph{DevArtist} a compiler-assisted patching tool for security vulnerabilities. This tool is capable of patching unsafe usage of randomness, sql injections and the usage of obsolete hashing functions such as MD5. Furthermore, it offers an application for end-users to harden their devices and it provides developers a mean to deliver more secure applications. In addition, the implementation of \emph{DevArtist} was analyzed thoroughly with automated testing on real applications already present in the Play Store, to better show its potential and discuss its limitations. In fact, in spite of the prototypical stage of this system, the evaluation suggests that such a tool reduces the exploitable attack surface of apps, which leads to less privacy leaks, hence aiding in the battle against Android malware.
\vfill
\hspace{0pt}
\pagebreak
