\chapter*{Acknowledgements}
\thispagestyle{empty}

I would like to thank my advisor Oliver for its great support and understanding, whenever we talked about a problem I was encountering, he always provided help and insights on how to go investigate deeper.\newline I would also like to thank Professor Micheal Backes and Fabio Massacci to take the time to review this work.\newline A special thank goes to my mum Melina, my aunt Nadia but also to my grand parents Angela and Emilio.\newline Big thanks also to all my friends who supported me for this three years, particular mention goes to: \'Abris Nagy, Istev\'an Seres, Riccardo Spadi, Francesco La Tegola, Artem Perlov and Roberto Zen. You guys rock!\newline Thanks and still many thanks to DUIR for their unconditional support during the whole time abroad: thanks to all of you guys for not replacing me, it meat a lot to me.\newline Huge thanks to the company which I worked for during the study on this work: Backes-SRT and in particular I would like to thank Sven Obser and Fabian Bendun, they provided a relaxing environment and an incredible support.\newline A special mention and thank goes to Sara Tacchetto for being at my side and to be always there in the darkest moments. Also, thanks for reading this work (and all the related powerpoints and talks) countless times.\newline There are a lot more people I should thank for accompanying me in this experience, but they would be too many to put here: you know who you are and you are all amazing people.